\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{enumitem}

\title{SolveIt Modern Build Notes}
\author{}
\date{}

\begin{document}
\maketitle

\section*{Overview}

SolveIt is a legacy MFC/OpenGL desktop application with a substantial numerical backend in Fortran and legacy CVODE/CVOde support. This repository has been migrated to a Visual Studio 2022 x64 build that targets Unicode and C++23 while preserving the existing application structure and behavior.

\section*{Current Status}

\begin{itemize}[leftmargin=*]
\item \texttt{SolveIt.vcxproj} is the primary modern build entry point.
\item \texttt{Debug|x64} and \texttt{Release|x64} are the validated target configurations.
\item Expected application outputs:
\begin{itemize}[leftmargin=*]
\item \texttt{x64/Debug/SolveIt.exe}
\item \texttt{x64/Release/SolveIt.exe}
\end{itemize}
\item The Intel oneAPI Fortran static libraries are built by \texttt{fortran/build\_top\_oneapi.ps1} and placed in \texttt{SolveIt.Lib/lib}.
\item The legacy CVODE/CVOde C sources are compiled into \texttt{x64/<Configuration>/cvode\_legacy.lib} by \texttt{SolveIt.Lib/lib/CVOde/build\_clang\_cl\_lib.ps1} during the project pre-link step.
\item The x64 build also generates \texttt{SolveIt.Lib/lib/dformt\_x64.lib} from \texttt{SolveIt.Lib/lib/dformt\_x64\_stub.c} via \texttt{SolveIt.Lib/lib/build\_dformt\_x64\_stub.ps1}.
\item \texttt{SolveIt.Lib/lib/CVOde/CVOdeShim.cpp} preserves the historical \texttt{CVODE::...} API that the application expects.
\end{itemize}

\section*{Prerequisites}

\begin{itemize}[leftmargin=*]
\item Visual Studio 2022 with MFC/ATL desktop C++ tooling
\item Visual Studio LLVM tools (\texttt{clang-cl}) for the legacy CVOde static library build
\item Intel oneAPI Fortran compiler (\texttt{ifx})
\item \texttt{vcpkg} packages for the x64 build, including \texttt{eigen3:x64-windows} and \texttt{spectra:x64-windows}
\item MiKTeX or another LaTeX distribution if you want to regenerate \texttt{README.pdf}
\end{itemize}

\section*{Build Workflow}

Build the Fortran libraries first:

\begin{verbatim}
powershell -ExecutionPolicy Bypass -File .\fortran\build_top_oneapi.ps1 -Configuration Debug
powershell -ExecutionPolicy Bypass -File .\fortran\build_top_oneapi.ps1 -Configuration Release
\end{verbatim}

Then build the application project:

\begin{verbatim}
MSBuild.exe .\SolveIt.vcxproj /p:Configuration=Debug /p:Platform=x64 /m /nologo
MSBuild.exe .\SolveIt.vcxproj /p:Configuration=Release /p:Platform=x64 /m /nologo
\end{verbatim}

Notes:

\begin{itemize}[leftmargin=*]
\item The x64 project automatically rebuilds \texttt{cvode\_legacy.lib} during pre-link.
\item The x64 project automatically regenerates \texttt{dformt\_x64.lib} during pre-link. The original \texttt{SolveIt.Lib/lib/dformt.LIB} is left in place for the legacy Win32 configuration only.
\item The validated modern target is x64. The older Win32 configuration is kept for reference, not as the primary migration target.
\end{itemize}

\section*{Migration Notes}

\begin{itemize}[leftmargin=*]
\item Unicode compatibility is handled at API boundaries rather than by a global string rewrite. The shared helpers live in \texttt{StdAfx.h}.
\item The legacy CVODE/CVOde wrapper headers were adjusted so their public C-facing types have stable C++ linkage.
\item High-value x64 warning cleanup has already been applied in several concentrated hotspots, including pointer-to-\texttt{long} payload storage in the rigid-body, tree, and plotting paths.
\item The legacy CVOde build still uses separate compilation with \texttt{clang-cl} in \texttt{gnu89} mode to avoid destabilizing the main C++ build.
\end{itemize}

\section*{Known Limitations}

\begin{itemize}[leftmargin=*]
\item The project still emits legacy warnings, mainly deprecated CRT calls, deprecated \texttt{strstream} usage, and older OpenGL or Win32 narrowing conversions.
\item The original \texttt{dformt.LIB} is a legacy x86 Digital/Compaq Visual Fortran archive. Current x64 builds do not consume symbols from it, so x64 now links against the generated \texttt{dformt\_x64.lib} placeholder instead.
\end{itemize}

\section*{Artifacts}

\begin{itemize}[leftmargin=*]
\item \texttt{README.md} is the primary plain-text documentation.
\item \texttt{README.pdf} is generated from this file with \texttt{pdflatex}.
\end{itemize}

\end{document}